Manuscript plots

### 2024-02-21 manuscript_modelling_and_plots.Rmd
adding the nasa tlx model

# priors based on Figalova et al (2023)
prior(normal(40, 20)) %>% 
  parse_dist() %>% 
  ggplot(aes(xdist = .dist_obj, y = prior)) + 
  stat_halfeye(.width = c(.5, .99)) +
  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
  scale_x_continuous(expression(italic(p)(beta[1]))) +
  theme_plot

@@

# fit 4 - random intercepts with priors on intercept (no n-back) and slope parameter (subjective workload)
nasa.fit.4 <- brm(data = nasa.tlx.mental %>%
                    dplyr::filter(participant != 34, participant != 39, participant != 47),
                  family = gaussian(), 
                  control = list(adapt_delta = 0.99999999999),
                 bf(converted_score ~ n_back + (1 | participant)),
                 prior = c(prior(normal(36, 20), class = Intercept),
                           prior(normal(40, 20), class = b)),
                 iter = 10000, warmup = 2000, chains = 4, cores = 2, seed = 13)

@@

>>>>

# priors based on Figalova et al (2023)
prior(normal(40, 20)) %>% 
  parse_dist() %>% 
  ggplot(aes(xdist = .dist_obj, y = prior)) + 
  stat_halfeye(.width = c(.5, .99)) +
  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
  scale_x_continuous(expression(italic(p)(beta[1]))) +
  theme_bw()

@@

# fit 4 - random intercepts with priors on intercept (no n-back) and slope parameter (effect of subjective workload)
nasa.fit.4 <- brm(data = nasa.tlx.mental %>%
                    dplyr::filter(participant != 34, participant != 39, participant != 47),
                  family = gaussian(), 
                  control = list(adapt_delta = 0.99999999999),
                 bf(converted_score ~ n_back + (1 | participant)),
                 prior = c(prior(normal(36, 20), class = Intercept),
                           prior(normal(40, 20), class = b)),
                 iter = 10000, warmup = 2000, chains = 4, cores = 2, seed = 13, file = here::here("gaze_entropy_heterogenous/plots/nasa_nback_model_4"))

@@

theme_bw() +
  theme(legend.position = "bottom", legend.direction = "horizontal", axis.title.x = element_text(size = 15), axis.text.x = element_text(size = 15), axis.title.y = element_text(size = 15), axis.text.y = element_text(size = 15), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), strip.text = element_text(face = "bold", size = 10))
